Towards Cloud Bursting for Extreme Scale Supercomputers\\ (Unrefereed Workshop Manuscript)

### 2014-06-30 paper/src/2_motivation.tex
Added comments in motication section, updated paper.tex for building

\section{Motivation and Background}

@@

Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access.
Since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from AMAZON.
We can see that the I/O throughput also grows as number of nodes grows but the aggregate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of interconnection inside supercomputer is quit larger than that from AMAZON.
%Also, if we compare the one nodes I/O throughput, 
Also if we compare Fig.~\ref{point to point connection LAB} with Fig.~\ref{throughput AMAZON to OURLAB}, the maximum throughput 
If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy\cite{AMAZON_AWS}, longer execution time means more cost.

>>>>

\section{Background and Motivation}
\label{sec:motivation}
\subsection{Public Cloud}
\label{sec:public_cloud}
\kento{Please explain what Public cloud is with example of Amazon EC2. Then, the details which is needed to mention for readers understand the rest of the sections.
  (1-1) Architecture (VM environment \& datacetners are geographically distributed)
  (1-2) Explain instance types which is related to this paper. Current draft does not mention any instance types.
  (1-3) introduce pay-as-you-go model to help readers understand the cost-based model in the modeling section 
  (1-4) [please add whatever you think it's needed]}

\subsection{Federation between supercomputers and clouds}
\kento{Please explain (2-1) how we federate supercomputers with clouds. $=>$ Virtualize supercomputer (e.g. TSUBAME V) + VM on clouds. 
                      (2-2) what the advantages are. $=>$ VMs can provide the same execution environment on both supercomputers and clouds
                      (2-3) [please add whatever you think it's needed]}

\subsection{Challenges in Federation with clouds}
\label{sec:problems}
\kento{In this section, (3-1) First explain I/O problems in federation with clouds based on the cloud architecture explained in the above (1-1) as well as using Fig.1-4. 
                        (3-2) Then, please briefly clarfy why ``(A) cloud-based burst buffer`` can improve I/O performance without using model. For example, parallel I/O, cacheing .... 
                              (Remember we knew that cloud-based burst buffer is effective before compareing the performances between w/ and w/o burst buffers by using performance model)
                        (3-3) Another challenge is a choice of instance types for burst buffer, and understanding the trade-off between I/O perfomrance and the monetary cost. 
                              In addtion, the choice of instances, the trade-offs are changes depending on given a supercomputer and cloud environments, such as network throughput, PFS performance. 
                              That's why the ``(B) perfomrance modeling`` is important}

\kento{Then, in the rest of the section, we explain (A) and (B)}

\subsection{(Current Section 2)}
\kento{Please fit the below sentences to the above sections with additional explanations}

\begin{table}[h]
\caption{\small XXXXX specification}
\label{tbl:spec}
\begin{center}
\begin{tabular}{|c|l|}
  \hline
  \cellcolor{lightgray} CPU   & Intel Core i7-3770K CPU (3.50 GHz x 4 cores)\\
  \hline
  \cellcolor{lightgray} Memory   & Cetus DDR3-1600 (16 GB)    \\
  \hline
  \cellcolor{lightgray} M/B   & GIGABYTE GA-Z77X-UD5H \\
  \hline
  \cellcolor{lightgray} SSD          & Crucial m4 CT256M4SSD3 (256GB,
  mSATA)\\
  \cellcolor{lightgray}             & (Peak read:500 MB/s, Peak write: 260
MB/s)
             \\
             \hline
             \cellcolor{lightgray} SATA converter & KOUTECH IO-ASS110 mSATA to 2.5' SATA  \\
             \cellcolor{lightgray}& Device Converter with Metal Frame \\
             \hline
             \cellcolor{lightgray} RAID Card    & Adaptec ASR-7805Q Single\\
             \hline

\end{tabular}
\end{center}
\end{table}
% vector figures
% Fig. 4 does not have a frame
% write machine spec

@@

Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes \kento{Describe node specification in Table I}, which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access.
Since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from AMAZON.
We can see that the I/O throughput also grows as number of nodes grows but the aggregate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of interconnection inside supercomputer is quit larger than that from AMAZON.
%Also, if we compare the one nodes I/O throughput, 
Also if we compare Fig.~\ref{point to point connection LAB} with Fig.~\ref{throughput AMAZON to OURLAB}, the maximum throughput \kento{??}
If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy\cite{AMAZON_AWS}, longer execution time means more cost.
